Incentivizing Exploration with Unbiased History

### 2018-10-26 3level.tex
notations

\begin{lemma}
  With probability at least $1 - \frac{4}{T^3}$, the following event
  $W_3$ holds: for all $a\in \{1, 2\}$ and $t\in [T]$, the empirical
  means of the first $t$ arm $a$ pulls is at most
  $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$.
\end{lemma}

>>>>

\begin{lemma}
  With probability at least $1 - \frac{4}{T^3}$, the following event
  $W_3$ holds: for all $a\in \{1, 2\}$ and $m \in [N_{T, a}]$, the
  empirical means of the first $t$ arm $a$ pulls is at most
  $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$, where $N_{T, a}$ is
  the total number of arm $a$ pulls by the end of $T$ rounds.
\end{lemma}
